---
title: "panel"
author: "Gonzalo Candel"
date: "23/4/2021"
output: html_document
---
# PANEL DATA REGRESION BY USING PRINCIPAL INDEXES

## 0. REFERENCES
http://www.urfie.net/read/index.html#page/5 

https://stats.stackexchange.com/questions/142091/how-to-cope-with-serial-correlation-and-time-effects-in-a-panel-data-model-in-r 
https://www.econometrics-with-r.org/6-3-mofimr.html

https://www.researchgate.net/post/How_can_I_correct_heteroscedasticity_from_my_Random_Effect_Two_way_Panel_Regression_Model-if_the_log_transformation_of_IV_does_not_help 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. LOADING DATA AND LIBRARIES

```{r,warning=FALSE,message=FALSE}
library(readxl)
library(dplyr)
library(plm)
library(sjPlot)
library(plotly)
library(broom)
library(reshape2)
library(tidyr)
library(corrplot)
setwd("C:/Users/Gonzalo/Documents/CURSO3/PRIII")
#panel = read_excel("integrada_sinNa.xlsx")
panel = read_excel("integrada2.xlsx")
datos_kaggle = panel %>% select(2,3,4,5,6,7,8,9,10,"Family")
#datos_kaggle = panel[,2:10]
colnames(datos_kaggle) = c("country","hpscore","loggdp","health","freedom","trust","generosity","dystopia","year","family")
```

## 2. CHECKING FOR CORRELATION IN INDEXES AND FIRST LINEAR MODEL (POOLING)

```{r}
M = cor(datos_kaggle[,c(2,3,4,5,6,7,8,10)])
corrplot(M,method="number")
panel_datos_kaggle = pdata.frame(datos_kaggle,index=c("country","year"))
pool = plm(hpscore ~ loggdp + health + freedom + trust + generosity + dystopia + family, data=panel_datos_kaggle,model="pooling")
summary(pool)
```
Graficking the weights of the model and the effect of the combination of both weigths and input data:
```{r}
#lm = lm(cnt ~ .,data=days2)

broom::tidy(pool) %>% 
  mutate(term = forcats::fct_reorder(term, estimate)) %>% 
  plot_ly(x = ~estimate, y = ~term,hoverinfo="none") %>%
  add_markers(error_x = ~list(value = std.error),color = I("black"))

coefs = pool$coefficients[2:length(pool$coefficients)]
effects = panel_datos_kaggle %>% select(names(coefs))
variables = names(coefs)
for (i in (1:length(coefs))){
  var = variables[i]
  effects[,var] = coefs[i]*panel_datos_kaggle[,var]}

effects2 = melt(effects,id.vars=0)
g2 = ggplot(data=effects2,aes(x=value,y=reorder(variable,value, FUN = mean, na.rm=TRUE))) + stat_boxplot(geom ='errorbar',colour="dodgerblue2")+ geom_boxplot(fill="lightblue",colour = "blue",outlier.colour = "dodgerblue2")+ylab("reoreder(variable,value)") 
g2
```

```{r}
#bonf = pairwise.t.test(panel_datos_kaggle$hpscore,panel_datos_kaggle$year,p.adj="none")
#bonf
```

### 2.1. WITHIN INDIVIDUAL EFFECTS MODEL
Conclusion: Not meaningful effects as the model R2 is practically 0.
```{r}
dg = plm(hpscore ~ loggdp + health + freedom + trust + generosity + dystopia + family, data=panel_datos_kaggle,model="within",effect="individual")
summary(dg)
#summary(fixef(dg,type="level"))
```
### 2.2. RANDOM EFFECTS MODEL

```{r}
rd = plm(hpscore ~ loggdp + health + freedom + trust + generosity + dystopia + family, data=panel_datos_kaggle,model="random")
summary(rd)
```
#### DIFFERENT TESTS OVER THE MODELS DONE BEFORE
```{r}
plmtest(pool,type=c("bp")) #sí que hay efectos de panel
```

```{r}
pFtest(dg,pool) #hay diferencias significativas entre países
```

```{r}
phtest(dg,rd) #hay diferencias significativas entre países
```
### 2.3. TEMPORAL EFFECTS MODEL (WITHIN)
```{r}
dg2 = plm(hpscore ~ loggdp + health + freedom + trust + generosity + dystopia + family, data=panel_datos_kaggle,model="within",effect="time")
summary(dg2)
summary(fixef(dg2,type="level"))
```
```{r}
pFtest(dg2,pool)
```
```{r,warning=FALSE,message=FALSE}
library(lmtest)
bptest(hpscore ~ loggdp + health + freedom + trust + generosity + dystopia + factor(year),data=panel_datos_kaggle,studentize = F) #existe heterocesaticidad
```
```{r}
coeftest(dg2, vcovHC) #coeficientes robustos heterocedasticidad
```

```{r}
a = list(title="Feature")
b = list(title="Weight estimate")
plt = broom::tidy(coeftest(dg2,vcovHC)) %>% 
  mutate(term = forcats::fct_reorder(term, estimate)) %>% 
  plot_ly(x = ~estimate, y = ~term) %>%
  add_markers(error_x = ~list(value = std.error),color = I("black")) %>% layout(title="Weight plot",xaxis=b,yaxis=a) 
plt
#broom::tidy(dg2) %>% 
#  mutate(term = forcats::fct_reorder(term, estimate)) %>% 
#  plot_ly(x = ~estimate, y = ~term,hoverinfo="none") %>%
#  add_markers(error_x = ~list(value = std.error),color = I("black"))

coefs = dg2$coefficients
effects = panel_datos_kaggle %>% select(names(coefs))
variables = names(coefs)
for (i in (1:length(coefs))){
  var = variables[i]
  effects[,var] = coefs[i]*panel_datos_kaggle[,var]}

effects2 = melt(effects,id.vars=0)
g2 = ggplot(data=effects2,aes(x=value,y=reorder(variable,value, FUN = mean, na.rm=TRUE))) + stat_boxplot(geom ='errorbar',colour="dodgerblue2")+ geom_boxplot(fill="lightblue",colour = "blue",outlier.colour = "dodgerblue2")+ylab("Feature")+xlab("Feature effect") + labs(title="Effect plot")
g2
```
```{r}
htmlwidgets::saveWidget(as_widget(plt), "weightplot.html") #exporting weightplot as html (plotly)
```



```{r}
predict(dg2,panel_datos_kaggle)
```

```{r}
library(ggeffects)
ggpredict(dg2)
```
```{r}
library(caret)
postResample(predict(pool,datos_kaggle),datos_kaggle$hpscore)
```
```{r}

```

